\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\setstretch{1.05}

\begin{document}
	
	\begin{center}
		{\Large \textbf{Publication List}}\\[6pt]
		{\large Hanwen Zhang}
	\end{center}
	
	\vspace{1em}
	
	\begin{enumerate}[leftmargin=1.5em, itemsep=0.6em]
		
		\item \textbf{H. Zhang}. \textit{“Constructing optimal Wannier functions via potential theory, Part II: isolated multiband for matrix models.”} (To be submitted.)
		
		\item \textbf{H. Zhang}. \textit{“A highly accurate procedure for computing globally optimal Wannier functions in one-dimensional crystalline insulators, Part II.”} (To be submitted.)
		
		\item \textbf{H. Zhang}. \textit{“Constructing optimal Wannier functions via potential theory: isolated single band for matrix models.”} \href{https://arxiv.org/abs/2502.08641}{\color{blue} \emph{Preprint} }(2025).
		
		\item A. Gopal, \textbf{H. Zhang}. \textit{“A highly accurate procedure for computing globally optimal Wannier functions in one-dimensional crystalline insulators.”} \href{https://link.springer.com/article/10.1007/s10444-025-10266-4}{\color{blue}  \emph{Advances in Computational Mathematics}},   \href{https://arxiv.org/abs/2409.04369}{\color{blue} \emph{Preprint} }(2025)
		
		\item \textbf{H. Zhang}, V. Rokhlin. \textit{“Finding roots of complex analytic functions via generalized colleague matrices.”} \href{https://link.springer.com/article/10.1007/s10444-024-10174-z}{\color{blue}  \emph{Advances in Computational Mathematics}},    \href{https://arxiv.org/abs/2307.14494}{\color{blue} \emph{Preprint} }(2024).
		
		\item W. Xue, \textbf{H. Zhang}, A. Gopal, V. Rokhlin, O. Miller. \textit{“Fullwave design of cm-scale cylindrical metasurfaces via fast direct solvers.”} \href{https://arxiv.org/abs/2308.08569}{\color{blue} \emph{Preprint} }(2023).
		
		\item \textbf{H. Zhang}, Z. Kuang, S. Puri, and O. Miller. \textit{“Conservation-law-based global bounds to quantum optimal control.”} \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.127.110506}{\color{blue}  \emph{Physical Review Letters}},    \href{https://arxiv.org/abs/2105.06054}{\color{blue} \emph{Preprint} }(2021).

		
		\item \textbf{H. Zhang}, O. Miller. \textit{“Quasinormal coupled mode theory.”}  \href{https://arxiv.org/abs/2010.08650}{\color{blue} \emph{Preprint} }(2020).
		
		\item \textbf{H. Zhang}, C.-W. Hsu, and O. Miller. \textit{“Scattering concentration bounds: brightness theorems for waves.”} \href{https://opg.optica.org/optica/fulltext.cfm?uri=optica-6-10-1321}{\color{blue}  \emph{Optica}},    \href{https://arxiv.org/abs/1810.02727}{\color{blue} \emph{Preprint} }(2019).
		
		\item Solutions manual to \textit{Quantum Mechanics} by Julian Schwinger with Berthold-Georg Englert. (To appear.)
		
	\end{enumerate}
	
\end{document}
